---
title: "MATH 3070 Lab Project 3"
author: "Your Name"
date: "September 8, 2016"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 2.43)
*The `time` variable in the `nym.2002` data set (**UsingR**) contains the time to finish the 2002 New York City Marathon for a random sample of the finishers.*

1. *What percent ran the race in under 3 hours?*

```{r}
# Your code here
```

2. *What is the time cutoff for the top 10%? The top 25%?*

```{r}
# Your code here
```

3. *What time cuts off the bottom 10%?*

```{r}
# Your code here
```

## Problem 2 (Verzani problem 4.1)
*The data set `UScereal` (**MASS**) contains data on cereals sold in the United States in 1993. For this data set, answer the following questions:*

1. *How many rows does the data frame have? Columns?*

```{r}
# Your code here
```

2. *How many different manufacturers are included?*

```{r}
# Your code here
```

3. *How many vitamin categories are included?*

```{r}
# Your code here
```

4. *How many cereals have a sugar level above 10?*

```{r}
# Your code here
```

5. *What is the mean calorie value for cereals with more than 5 grams of fat? Less than or equal to 5?*

```{r}
# Your code here
```

6. *What is the mean calorie value for cereals on the middle shelf (2)?*

```{r}
# Your code here
```

## Problem 3 (Verzani problem 4.2)
*R uses lists for many purposes behind the scenes. For example, the output of `lm(mpg ~ wt, data=mtcars)` returns a list. Create this object, then answer the following:*

1. *How many components does this list have?*

```{r}
# Your code here
```

2. *What are the names of the components?*

```{r}
# Your code here
```

3. *What kind of data is held in the `residuals` variable?*

```{r}
# Your code here
```

## Problem 4
*Create a data frame containing the data in the following table:*

| First    | Last      | Age |
|----------|-----------|-----|
| Marcus   | Holstein  | 23  |
| Samuel   | Adams     | 56  |
| Gus      | McPherson | 43  |
| Margaret | Olsen     | 41  |
| Zim      | Newbold   | 95  |

```{r}
# Your code here
```