---
title: "MATH 3070 Lab Project 5"
author: "Pranav Rajan"
date: "October 1, 2020"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 5.1)
*For the `UScereal` (**MASS**) data set, create a scatter plot of `calories` modeled by `sugars` using the `shelf` variable to create different plot characters. Add a legend to indicate the shelf number. Is there any patterns? (Use base R plotting for this problem.)*

```{r, tidy=TRUE, error=TRUE}
# Your code here
suppressMessages(library(UsingR))
require(UsingR)
with(UScereal,
     plot(calories, sugars,
          # make character dependent on shelf
          pch = as.numeric(shelf),
          col = as.numeric(shelf),
          
          # labels for stuff
          xlab="sugars", ylab="calories", main="sugars vs. calories"))

# add legend
legend(370, 10, legend=c("Shelf 1", " Shelf 2", "Shelf 3"),
       col = 1:3,
       pch = 1:3)
```

## Problem 2 (Verzani problem 5.3)
*For the data set `UScereal` (**MASS**) make a pairs plot of the numeric variables. Which correlation looks larger: fat and calories or fat and sugars?*

```{r, tidy=TRUE, error=TRUE}
# Your code here
suppressMessages(library(UsingR))
suppressMessages(library(dplyr))
require(usingR)
require(dplyr)
data <- UScereal
numericData <- select_if(data, is.numeric)
pairs(numericData,
      # color code by fat variable
      col=numericData$fat)
```

## Problem 3 (Verzani problem 5.4)
*For the data set `batting` (**UsingR**) make a bubble plot of home runs hit (`HR`) modeled by hits (`H`) where the scale factor for each point is given by `sqrt(SO)/10`. Is there any story to be told by the size of the points? (You must use base R plotting for this problem.)*

```{r, tidy=TRUE, error=TRUE}
# Your code here
suppressMessages(library(UsingR))
require(UsingR)
plot(HR ~ H, data=batting,
     # filled circles
     pch=16,
     # color for the circles
     col=rgb(red = 0, green =0, blue = 0, alpha = 0.250),
     # scale factor
     cex= sqrt(SO)/10)
```

