---
title: "MATH 3070 Lab Project 6"
author: "Pranav Rajan"
date: "October 2, 2020"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 5.6)
*For the `batting` (**UsingR**) data set, make parallel boxplots of the batting average (`H/AB`) for each team. Which team had the greatest median average? (Use **lattice** functions for this problem.)*

```{r, tidy=TRUE, error=TRUE}
# Your code here
suppressMessages(library(UsingR))
suppressMessages(library(lattice))
require(UsingR)
library(lattice)
battingAverage <- batting$H/batting$AB
bwplot(batting$teamID ~ battingAverage, data=batting)
```

## Problem 2 (Verzani problem 5.7)
*For the `mtcars` data set, produce graphics of the following using **ggplot2**:*

1. *Boxplots for miles per gallon (`mpg`) for groups defined by the number of gears (`gear`).*

```{r, tidy=TRUE, error=TRUE}
# Your code here
suppressMessages(library(UsingR))
require(UsingR)
ggplot(mtcars, aes(group=gear, x=gear, y=mpg)) + geom_boxplot()
```

3. *A scatterplot of `mpg` modeled by horsepower (`hp`). Create facets by the number of cylinders (`cyl`) and `gear`.*

```{r, tidy=TRUE, error=TRUE}
# Your code here
suppressMessages(library(ggplot2))
library(ggplot2)
ggplot(mtcars, aes(x=hp, y=mpg)) + geom_point() + facet_grid(cyl ~ gear)
```

## Problem 3
*Using the `batting` data set (UsingR), create a visualization that does the following:*

* *Plots the* rate *of intentional walks (that is, the number of intentional walks divided by the number of times a player was at bat; these are the `IBB` and `AB` variables in the data set, respectively) against the* rate *of home runs (the `HR` variable in the data set) as a scatter plot*

* *Draws a trend line for these variables*

* *Identifies and labels the outlier in the data set in these variables (easily spotted once the scatter plot is drawn)*

*(Hint: `geom`-type functions can accept data arguments and will use the data set passed rather than the default for the chart. So for the third requirement, consider adding a text layer with `geom_text(data = ..., aes(...))` where the argument passed to `data` is a subset of the data set consisting of the outlier, and `aes(...)` defines how to label that outlier.)*

```{r, tidy = TRUE, error=TRUE}
# Your code here
suppressMessages(library(UsingR))
require(UsingR)
intentionalWalkRate <- batting$IBB/batting$AB
ggplot(batting, aes(x=HR, y=IBB/AB)) + geom_point() + geom_smooth(method=lm, fullrange=TRUE)

```


## Problem 4
*Reconsider the data set from a previous project containing data about the results of 2012 Olympics. I load the data in for you below:*

```{r}
olympic2012 <- read.csv("http://introcs.cs.princeton.edu/java/data/olympic-medals2012.csv")
```

*Use any plotting system (base R, **lattice**, **ggplot2**) to create plot involving at least three variables in the `olympic2012` data set, showing a relationship not yet visualized in the lecture, the textbook, or this assignment. Explain the relationship you explored and any interesting findings. **Bonus points will be given for plots that I consider exceptionally clean, clear, and insightful, accompanied with good analyses of what you found.***

```{r, tidy=TRUE, error=TRUE}
# Your code here
bronze <- olympic2012$Bronze.Per.100K.pop
silver <- olympic2012$Silver.Per.100K.pop
gold <- olympic2012$Gold.Per.100K.pop
country <- olympic2012$Country.name
df <- data.frame(bronze, silver, gold, row.names=country)

# plot a heat map
plotmat <- sapply(df, scale)
rownames(plotmat) <- rownames(df)
heatmap(plotmat, Rowv = NA, Colv = NA)

# The heat map is a numeric matrix with the bronze, 
# silver and gold medals per 100,000 people in the 
# population standardized for each variable 
# where the mean was subtracted from each observation, and then divided by the standard deviation
# The countries are on the y axis 
# The bronze, silver and gold categories are on the
# x axis.
# An interesting finding was that there were that France did not have a lot of gold, silver
# and bronze medals per 100,000 people even though the French are really successful in 
# Olympic sports. I also think that there is something off by this chart because there
# should be a lot more countries (the United States is missing for example). # It might be interesting to group the countries by continent for the data.

```