---
title: "MATH 3070 Lab Project 7"
author: "Pranav Rajan"
date: "October 21, 2020"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 3.2)
*For the `michelson` (**MASS**) data set, produce a density plot comparing `Speed` between Experiments 1 and 2.*

```{r, tidy=TRUE, error=TRUE}
# Your code here
suppressMessages(library(UsingR))
require(UsingR)
speed <- michelson$Speed
expt <- michelson$Expt
first <- speed[expt == 1]
second <- speed[expt == 2]

d_1 <- density(first)
d_2 <- density(second)
xrange <- range(c(d_1$x, d_2$x))
yrange <- range(c(d_1$y, d_2$y))
plot(d_1, xlim=xrange, ylim=yrange, xlab="densities", main="Densities of Different Experiments")
lines(d_2, lty=2)
```

## Problem 2 (Verzani problem 3.4)
*Three students record the time spent on homework per class. Their data is:*

| Student| 1  | 2  | 3  | 4  | 5 |
|:-------|---:|---:|---:|---:|--:|
| Marsha | 25 | 0  | 45 | 90 | 0 |
| Bill   | 30 | 30 | 30 | 30 |   |
| Holly  | 15 | 0  | 90 | 0  |   |

*Use a list to store these values. Then create a boxplot to compare. (You must use `boxplot()`'s formula interface for this problem.)*

```{r, tidy=TRUE, error=TRUE}
# Your code here
times <- c(25, 0, 45, 90, 0, 30, 30, 30, 30, 15, 0, 90, 0)
students <- rep(c("Marsha", "Bill", "Holly"), times=c(5, 4, 4))
boxplot(times ~ students, data = list(times, students))
```

## Problem 3 (Verzani problem 3.5)
*A group of nursing students take turns measuring some basic assessments. Their data is:*

|          | Temp | Pulse | Systolic | Diastolic |
|----------|------|-------|----------|-----------|
| Jackie   | 98.2 | 96    |  134     | 90        |
| Florence | 98.6 | 56    |  120     | 80        |
| Mildred  | 98.2 | 76    |  150     | 95        |

*Create a data frame of these values. Will `plot()` and `boxplot()` produce the same graphic?*

```{r, tidy=TRUE, error=TRUE}
# Your code here
Students <- c("Jackie", "Florence", "Mildred")
Temp <- c(98.2, 98.6, 98.2)
Pulse <- c(96, 56, 76)
Systolic <- c(134, 120, 150)
Diastolic <- c(90, 80, 95)
df <- data.frame(Temp, Pulse, Systolic, Diastolic, row.names = Students)
plot(df)
boxplot(df)
# The charts are different with the plot function producing a trellis layout
# the boxplot produces a set of standard boxplot visualizations
```

## Problem 4 (Verzani problem 3.8)
*The second argument to `split` can be a list of factors. The result is that all interactions (possible combinations) are used for the groups. In the `ToothGrowth` data set, growth (`len`) is measured for two types of supplements (`supp`) and three doses (`dose`). Split this `len` value into 6 groups.*

```{r, tidy=TRUE, error=TRUE}
# Your code here
split(ToothGrowth$len, list(ToothGrowth$supp, ToothGrowth$dose))
```