---
title: "MATH 3070 Lab Project 7"
author: "Pranav Rajan"
date: "October 21, 2020"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 3.2)
*For the `michelson` (**MASS**) data set, produce a density plot comparing `Speed` between Experiments 1 and 2.*

```{r, tidy=TRUE, error=TRUE}
# Your code here
require(UsingR)
str(michelson)
len_split <- with(michelson, split(Speed, Expt))
expt1 <- len_split$"1"
expt2 <- len_split$"2"
plot(density(expt1), lty= 1)
lines(density(expt2), lty=2)
```

## Problem 2 (Verzani problem 3.4)
*Three students record the time spent on homework per class. Their data is:*

| Student| 1  | 2  | 3  | 4  | 5 |
|:-------|---:|---:|---:|---:|--:|
| Marsha | 25 | 0  | 45 | 90 | 0 |
| Bill   | 30 | 30 | 30 | 30 |   |
| Holly  | 15 | 0  | 90 | 0  |   |

*Use a list to store these values. Then create a boxplot to compare. (You must use `boxplot()`'s formula interface for this problem.)*

```{r, tidy=TRUE, error=TRUE}
# Your code here
times <- c(25, 0, 45, 90, 0, 30, 30, 30, 30, 15, 0, 90, 0)
students <- rep(c("Marsha", "Bill", "Holly"), times=c(5, 4, 4))
theData <- list(time = times, student = students)
boxplot(time ~ student, data = theData)
```

## Problem 3 (Verzani problem 3.5)
*A group of nursing students take turns measuring some basic assessments. Their data is:*

|          | Temp | Pulse | Systolic | Diastolic |
|----------|------|-------|----------|-----------|
| Jackie   | 98.2 | 96    |  134     | 90        |
| Florence | 98.6 | 56    |  120     | 80        |
| Mildred  | 98.2 | 76    |  150     | 95        |

*Create a data frame of these values. Will `plot()` and `boxplot()` produce the same graphic?*

```{r, tidy=TRUE, error=TRUE}
# Your code here
Jackie <- c(98.2, 96, 134, 90)
Florence <- c(98.6, 56, 120, 80)
Mildred <- c(98.2, 76, 150, 95)
theData <- data.frame(Jackie, Florence, Mildred)
plot(theData)
boxplot(theData)
```

## Problem 4 (Verzani problem 3.8)
*The second argument to `split` can be a list of factors. The result is that all interactions (possible combinations) are used for the groups. In the `ToothGrowth` data set, growth (`len`) is measured for two types of supplements (`supp`) and three doses (`dose`). Split this `len` value into 6 groups.*

```{r, tidy=TRUE, error=TRUE}
# Your code here
str(ToothGrowth)
len <- ToothGrowth$len
supp <- ToothGrowth$supp
dose <- ToothGrowth$dose
split(len, list(supp, dose))
```