---
title: "MATH 3070 Lab Fall Project 2 Solutions"
author: "Pranav Rajan"
date: "September 10, 2020"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 2.4)
*Create the following sequences, using `:`, `seq()`, or `rep()` as appropriate:*

1. `"a" "a" "a" "a" "a" "a"`

```{r}
# Your solution here
rep("a", 6)
```

2. `1 3 ... 99` *(the odd numbers)*

```{r}
# Your solution here
seq(1, 100, by=2)
```

3. `1 1 1 2 2 2 3 3 3`

```{r}
# Your solution here
rep(c(1, 2, 3), times=c(3, 3, 3))
```

## Problem 2 (Verzani problem 2.3)
*Let our small data set be* `2 5 4 10 8`.

1. *Enter this data into a data vector `x`.*

```{r}
# Your code here
x <- c(2, 5, 4, 10, 8)
```

2. *Find the square of each number.*

```{r}
# Your code here
x^2
```

3. *Subtract 6 from each number.*

```{r}
# Your code here
x - 6
```

4. *Subtract 9 from each number and then square the answer.*

```{r}
# Your code here
(x - 9)^2
```

## Problem 3 (Verzani problem 2.25)
*Write a function `isprime()` that checks if a number $x$ is prime by dividing $x$ by all the values in $2, ..., x - 1$ then checking to see if there is a remainder of 0. The expression `a %% b` returns the remainder of `a` divided by `b`.*

```{r}
# Your code here
isprime <- function(x) {
  y <- seq(2, x-1)
  for (value in y) {
    if (x %% value == 0)
      return("False")
  }
  return("True")
}
isprime(7)
```

***BONUS:** You do not need to check all numbers from 2 to $x - 1$ to see if a number is prime. What is the largest you would need to go for an arbitrary $x$? Create a new function, `isprime2()`, that implements this better (yet still slow) method.*

```{r}
# Your code here
```

## Problem 4 (Verzani problem 2.32)
*Fit a density estimate to the data set `pi2000` (**UsingR**). Compare with the appropriate histogram. Why might you want to add an argument like `breaks = 0:10-.5` to `hist()`? (Hint: read the documentation of `hist()` to see what setting this argument does.)*

```{r}
# Your code here
require("UsingR")
# density plot
pi2000density <- density(pi2000)
# histogram plot
# the breaks parameter defines the spacing between bars or the number of bars
pi2000hist <- hist(pi2000, breaks= 0:10 - 0.5)

plot(pi2000density)
plot(pi2000hist)
```

## Problem 5 (Verzani problem 2.34)
*The data set `DDT` (**MASS**) contains independent measurements of the pesticide DDT on kale. Make a histogram and a boxplot of the data. From these, estimate the mean and standard deviation. Check your answers with the appropriate functions.*

```{r}
# Your code here
require("UsingR")
histogramChart <- hist(DDT)
#plot(histogramChart)
boxplotChart <- boxplot(DDT, main="DDT Kale Data", ylab="kale mass")

# Estimates
# Mean: 3.25 based on the boxplot
# SD: roughly 0.5 based on sorting the data since the points seem really close 
# print(sort(DDT))

# Actual data summary
mean(DDT)
sd(DDT)
```
