---
title: "MATH 3070 Lab Project 3"
author: "Pranav Rajan"
date: "September 13, 2020"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 2.43)
*The `time` variable in the `nym.2002` data set (**UsingR**) contains the time to finish the 2002 New York City Marathon for a random sample of the finishers.*

1. *What percent ran the race in under 3 hours?*

```{r}
# Your code here
suppressMessages(library(UsingR))
require("UsingR")

# get summary of the data
#str(nym.2002)

# There are 1000 observations of 5 variables
# the time vector
times <- nym.2002$time
# print the first 6 values of the time vector
#print(head(time))

# time is calculated in minutes
# calculate times less than 3 hours
result <- sum(times < (3 * 60))/length(times) * 100
print(result)
```

2. *What is the time cutoff for the top 10%? The top 25%?*

```{r}
# Your code here
quantile(times, c(0.1, 0.25))
```

3. *What time cuts off the bottom 10%?*

```{r}
# Your code here
quantile(times, c(0.9))
```

## Problem 2 (Verzani problem 4.1)
*The data set `UScereal` (**MASS**) contains data on cereals sold in the United States in 1993. For this data set, answer the following questions:*

1. *How many rows does the data frame have? Columns?*

```{r}
# Your code here
suppressMessages(library(UsingR))
require("UsingR")

# Rows
NROW(UScereal)

# Columns
NCOL((UScereal))
```

2. *How many different manufacturers are included?*

```{r}
# Your code here
# find all the unique manufacturers 
unique(UScereal$mfr)



```

3. *How many vitamin categories are included?*

```{r}
# Your code here
# find all the unique vitamin categories
unique(UScereal$vitamins)
```

4. *How many cereals have a sugar level above 10?*

```{r}
# Your code here
# get the sugar vector for the cereals (contains 65 values)
sugars <- UScereal$sugars
sum(sugars > 10)
```

5. *What is the mean calorie value for cereals with more than 5 grams of fat? Less than or equal to 5?*

```{r}
# Your code here
fat <- UScereal$fat

# fat greater than 5 grams
newData <- subset(UScereal, fat > 5)
newDataCalories <- mean(newData$calories)
print(newDataCalories)
# fat less <= 5
newData2 <- subset(UScereal, fat <= 5)
newDataCalories2 <- mean(newData2$calories)
print(newDataCalories2)
```

6. *What is the mean calorie value for cereals on the middle shelf (2)?*

```{r}
# Your code here
shelf2Cereals <- subset(UScereal, shelf == 2)
shelf2Calories <- shelf2Cereals$calories
mean(shelf2Calories)

```

## Problem 3 (Verzani problem 4.2)
*R uses lists for many purposes behind the scenes. For example, the output of `lm(mpg ~ wt, data=mtcars)` returns a list. Create this object, then answer the following:*

1. *How many components does this list have?*

```{r}
# Your code here
linearModel <- lm(mpg ~ wt, data=mtcars)
print(length(linearModel))
```

2. *What are the names of the components?*

```{r}
# Your code here
names(linearModel)
```

3. *What kind of data is held in the `residuals` variable?*

```{r}
# Your code here
# get the residual data component
residualsData <- linearModel["residuals"]
# determine the type of the residuals data component using the information from str()
typeof(residualsData$residuals)
```

## Problem 4
*Create a data frame containing the data in the following table:*

| First    | Last      | Age |
|----------|-----------|-----|
| Marcus   | Holstein  | 23  |
| Samuel   | Adams     | 56  |
| Gus      | McPherson | 43  |
| Margaret | Olsen     | 41  |
| Zim      | Newbold   | 95  |

```{r}
# Your code here
peopleData <- data.frame("First" = c("Marcus, Samuel, Gus, Margaret, Zim"), "Last" = c("Holstein", "Adams", "McPherson", "Olsen", "Newbold"), "Age" = c(23, 56, 43, 41, 95))
str(peopleData)
```