---
title: "MATH 3070 Lab Project 14"
author: "Pranav Rajan"
date: "December 8, 2020"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 9.2)
*The `samhda` (**UsingR**) data set contains information on marijuana usage among children as collected at the Substance Abuse and Mental Health Data Archive. The variable `marijuana` indicates whether the individual has ever tried marijuana. A 1 means yes, a 2 no. If it used to be that 50%  of the target population had tried marijuana, does this data indicate an increase in marijuana usage? Do a significance test of proportions to decide.*

```{r, tidy = TRUE}
# Your code here
suppressMessages(library(UsingR))
yes <- sum(samhda$marijuana == 1)
no <- sum(samhda$marijuana == 2)
print(yes)
print(no)
prop.test(yes, length(samhda$marijuana), p = 0.5)

# p value is near 0, so we reject the null hypothesis
```

## Problem 2 (Verzani problem 9.4)
*In the United States in 2007, the proportion of adults age 21-24 who had no medical insurance was 28.1 percent. A survey of 75 recent college graduates in this age range finds that 40 percent are without insurance. Does this support a difference from the nationwide proportion? Perform a test of significance and report the p-value. Is it significant? (Perform this test "by hand", not using `prop.test()`.)*

```{r, tidy = TRUE}
# Your code here
# Hypothesis + set up
n <- 75
p0 <- 0.281
p_hat <- 0.40
# test
z <- (p_hat - p0) / sqrt((p0 * (1 - p0)) / n)

#p value 
p_val <- 2 * pnorm(z, lower.tail = FALSE)
print(p_val)

# it is not significant
# reject the null hypothesis
```

## Problem 3 (Verzani problem 9.14)
*The data set `normtemp` (**UsingR**) contains measurements of 130 healthy, randomly selected individuals. The variable `temperature` contains normal body temperature. Does the data appear to come from a Normal distribution? If so, perform a $t$-test to see if the commonly assumed value of 98.6 degrees fahrenheit is correct. (Studies have suggested that 98.2 degrees fahrenheit is more accurate.)*

```{r, tidy = TRUE}
# Your code here
suppressMessages(library(UsingR))
t.test(normtemp$temperature, mu = 98.6)
# reject the null hypothesis since the value is super close to 0 
t.test(normtemp$temperature, mu = 98.2)

# 98.2 is a better value for approximating the normal distribution
```

## Problem 4 (Verzani problem 9.16)
*A one-sided, one-sample $t$-test will be performed. What sample size is needed to have a power of 0.80 for a significance level of 0.05 if `delta = 0.05` and the population standard deviation is assumed to be 5?*

```{r, tidy = TRUE}
# Your code here
power.t.test(power = 0.80, delta = 0.05, sd = 5, sig.level = 0.05, alternative="one.sided")
```

## Problem 5 (Verzani problem 9.31)
*For the `babies` (**UsingR**) data set, the variable `age` contains the recorded mom's age and `dage` contains the dad's age for several cases in the sample. Do a significance test of the null hypothesis of equal ages against a one-sided alternative that the dads are older in the sampled population.*

```{r, tidy = TRUE}
# Your code here
suppressMessages(library(UsingR))


```