---
title: "MATH 3070 Lab Fall Project 1"
author: "Pranav Rajan"
date: "September 10, 2020"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 1.1)
*Use R as you would a calculator to find numeric answers to the following:*

1. $1 + 2(3 + 4)$

```{r, tidy=TRUE, error=TRUE}
# Your solution here
1 + 2 * (3 + 4)
```

2. $4^3 + 3^{2 + 1}$

```{r, tidy=TRUE, error=TRUE}
# Your solution here
(4 ** 3) + 3**(2 + 1)
```

3. $\sqrt{(4 + 3)(2 + 1)}$

```{r, tidy=TRUE, error=TRUE}
# Your solution here
sqrt((4 + 3) * (2 + 1))
```

4. $\left(\frac{1+2}{3 + 4} \right)^2$

```{r, tidy=TRUE, error=TRUE}
# Your solution here
((1 + 2)/(3 + 4))^2
```

## Problem 2 (Verzani problem 1.4)
*Use R to compute the following:*

$$\frac{0.25 - 0.2}{\sqrt{0.2(1-0.2)/100}}$$

```{r, tidy=TRUE, error=TRUE}
# Your solution here
((0.25 - 0.2)/(sqrt(0.2 *(1 - 0.2)/100)))
```

## Problem 3 (Verzani problem 1.7)
*The `exec.pay` (**UsingR**) data set is available after loading the package **UsingR**. Load the package, and inspect the data set. Scan the values to find the largest one.*

```{r, tidy=TRUE, error=TRUE}
# Your solution here
suppressMessages(library(UsingR))
require(UsingR)
max(exec.pay)
```
